Manuscript

### 2015-04-17 inst/simulation/manuscript.Rmd
...

study <- getStudy(scenario="A")
limits <- extent(study$studyArea$boundary)
iterations <- as.integer(c(1,4,1,2,5,31))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year)
wdensities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, weightHabitats=T)

@@

#library(directlabels)

p <- ggplot(wdensitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(data=densitiesScaled, aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1)
#p <- direct.label(p)
p <- p + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2)))), trans="log10",
                       #breaks=c(10^-4.5, 10^-4, 10^-3.5, 10^-3, 10^-2.5),
                       breaks=trans_breaks("log10", function(x) 10^x),
                       #labels=c(expression(10^-4.5), expression(10^-4.0), expression(10^-3.5), expression(10^-3.0), expression(10^-2.5)), limits=c(10^-4.5, 10^-2.5)
                       labels=trans_format("log10", math_format(10^.x))
                       ) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) +
  theme(legend.position="bottom", legend.margin=unit(-2, units="line"),
        plot.margin=unit(c(-.5, 0, 0, -.5), units="line"))
#p <- direct.label(p)
saveFigure(p, "manuscript-figure-2a.png", width=17, height=7.2, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-2a.pdf", width=17, height=7.2, dpi=300)

@@

p <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0.01,0.01)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() +
  theme(panel.grid.major=element_line(colour="grey"), plot.margin=unit(c(0, 0, 0, -.5), units="line"))
saveFigure(p, "manuscript-figure-2b.png", width=17, height=6.7, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-2b.pdf", width=17, height=6.7, dpi=300)
```

@@

plotPopulationSizesTable <- function(logTable) {
  library(reshape2)
  facet_labeller <- function(variable, value) {
    measured <- list(EstTrue=expression(alpha), Slope=expression(beta), R2=expression(R^2), Failed="Failed (%)")
    print(paste0(variable,"=",value))
    if (variable=="variable") return(measured[value])
    if (variable=="Case") return(paste("Case", value))
  }
  #x <- melt(logTable, id.vars=c("Scenario", "Model", "Case"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))
  x <- melt(logTable, id.vars=c("Scenario", "Model"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))

@@

>>>>

study <- getStudy(scenario="A")
limits <- extent(study$studyArea$boundary)
iterations <- as.integer(c(1,4,1,2,5,34))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year)
wdensities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, weightHabitats=T)

@@

@@

p1 <- ggplot(wdensitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(data=densitiesScaled, aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2)))), trans="log10",
                       #breaks=c(10^-4.5, 10^-4, 10^-3.5, 10^-3, 10^-2.5),
                       breaks=trans_breaks("log10", function(x) 10^x),
                       #labels=c(expression(10^-4.5), expression(10^-4.0), expression(10^-3.5), expression(10^-3.0), expression(10^-2.5)), limits=c(10^-4.5, 10^-2.5)
                       labels=trans_format("log10", math_format(10^.x))
                       ) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) +
  theme(legend.position="bottom", legend.margin=unit(-2, units="line"), legend.title=element_text(size=10), legend.text=element_text(size=10),
        plot.margin=unit(c(-3, 0, 0, -.5), units="line")) #top, right, bottom, and left margins
g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g1, "manuscript-figure-2a.png", width=17, height=8.8, dpi=200) # draft quality
saveFigure(g1, "manuscript-figure-2a.pdf", width=17, height=8.8, dpi=300)

p2 <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey") +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5), expand=c(0.01,0.01)) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal() +
  theme(panel.grid.major=element_line(colour="grey"),
        plot.margin=unit(c(0, 0, 0, -.5), units="line")) #top, right, bottom, and left margins
g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g2, "manuscript-figure-2b.png", width=17, height=6.9, dpi=200) # draft quality
saveFigure(g2, "manuscript-figure-2b.pdf", width=17, height=6.9, dpi=300)

p <- arrangeGrob(g1, g2)
saveFigure(p, "manuscript-figure-2.png", width=17, height=17, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-2.pdf", width=17, height=17, dpi=300)

@@

plotPopulationSizesTable_DEPRECATED <- function(logTable) {
  library(reshape2)
  facet_labeller <- function(variable, value) {
    measured <- list(EstTrue=expression(alpha), Slope=expression(beta), R2=expression(R^2), Failed="Failed (%)")
    print(paste0(variable,"=",value))
    if (variable=="variable") return(measured[value])
    if (variable=="Case") return(paste("Case", value))
  }

  #x <- melt(logTable, id.vars=c("Scenario", "Model", "Case"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))
  x <- melt(logTable, id.vars=c("Scenario", "Model"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))

@@

plotPopulationSizesTable <- function(logTable) {
  library(reshape2)
  library(dplyr)
  library(gtable)
  library(gridExtra)

  x <- melt(logTable, id.vars=c("Scenario", "Model"), measure.vars=c("EstTrue", "Slope", "R2", "Failed"))

  bestFit <- data.frame(variable=unique(x$variable), y=c(0, 1, 1, 0))
  errorBars <- x
  errorBars$value <- NA
  errorBars$value[errorBars$variable=="EstTrue"] <- logTable$EstTrue
  errorBars$qmin[errorBars$variable=="EstTrue"] <- logTable$EstTrueMin
  errorBars$qmax[errorBars$variable=="EstTrue"] <- logTable$EstTrueMax

  p1 <- x %>% filter(variable=="EstTrue") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=0), aes(yintercept=y), color="darkgray") + 
    geom_errorbar(data=errorBars, aes(Scenario, group=Model, ymax=qmax, ymin=qmin), position=position_dodge(width=.7), colour="darkgray") +
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(alpha)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line")) #top, right, bottom, and left margins
  g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, just="left", gp=gpar(fontsize=10)))

  p2 <- x %>% filter(variable=="Slope") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=1), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(beta)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line"))
  g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, just="left", gp=gpar(fontsize=10)))

  p3 <- x %>% filter(variable=="R2") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=1), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab(expression(R^2)) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line"))
  g3 <- arrangeGrob(p3, main=textGrob("c)", x=0.01, just="left", gp=gpar(fontsize=10)))

  p4 <- x %>% filter(variable=="Failed") %>%
    ggplot(aes(Scenario, value, group=Model)) +
    geom_hline(data=data.frame(y=0), aes(yintercept=y), color="darkgray") + 
    geom_point(aes(shape=Model), position=position_dodge(width=.7)) +
    xlab("") + ylab("Failed (%)") + ylim(0,100) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"),
                                        legend.title=element_text(size=10), legend.position="none",
                                        strip.text.x=element_text(size=10), strip.text.y=element_text(size=10),
                                        plot.margin=unit(c(0, 0.2, -.75, 0), units="line"))
  g4 <- arrangeGrob(p4, main=textGrob("d)", x=0.01, just="left", gp=gpar(fontsize=10)))

  legend <- gtable_filter(ggplot_gtable(ggplot_build(p1 + theme(legend.position="bottom", legend.margin=unit(-1, units="line")))), "guide-box")
  lheight <- sum(legend$height)
  p <- arrangeGrob(g1, g2, g3, g4, ncol=2)
  theight <- unit(10, "points")
  p <- arrangeGrob(p, textGrob("Scenario", gp=gpar(fontsize=10)), heights=unit.c(unit(1, "npc") - theight, theight))
  p <- arrangeGrob(p, legend, heights=unit.c(unit(1, "npc") - lheight, lheight), ncol=1)
